---
title: "Covid 19 Data Analysis"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
pacman::p_load(pacman, dplyr, GGally, ggplot2, ggthemes, 
               ggvis, httr, lubridate, plotly, rio, rmarkdown, shiny, 
               stringr, tidyr, reticulate, tidyverse, psych)
```

# COVID 19 Dataset

We have taken a small dataset of Covid-19, just for your understaning purpose. You have to work on the original dataset which contains about 19000 rows. The data used here is till 29-April-2020 and has records as on 29-April-2020. This data is available as a CSV file, downloaded from Kaggle. We will analyze this data.

```{r include=FALSE}
covid <- read_csv("C:/Users/user/Projects/Data-Analysis-Projects/Covid 19 Data Analysis/CovidData.csv")
```

```{r}
head(covid)
```

```{r}
describe(covid)
```

```{r}
covid |> colnames()
```

```{r}
covid |> str()
```

```{r}
is.na(covid) |> colSums()
```

## \### Lets run some Analysis to view somw certain Updates. Firstly we would want to see the heatmap of the null values.

```{python}
import seaborn as sns
import matplotlib.pyplot as plt
sns.heatmap(r.covid.isnull())
plt.show()
```

## Lets go into solving real life Questions.

### Q.1 ) Show the number of Confirmed , Deaths and Recovered cases in each Region.

```{r}
covid |> group_by(Region) |> reframe(COnfirmed = sum(Confirmed), Deaths = sum(Deaths), Recovered = sum(Recovered))
```

### Q2) Remove all the records where Confirmed Cases is Less Than 10.

```{r}
covids <- covid |> filter(Confirmed > 10)
```

```{r}
covids
```

### Q.3) In which Region, maximum number of Confirmed cases were recorded ?

```{r}
covid |> group_by(Region) |> summarise(Confirmed = sum(Confirmed)) |> arrange(desc(Confirmed))
```

### Q.4) In which Region, minimum number of Deaths cases were recorded ?

```{r}
covid |> group_by(Region) |> summarise(Deaths = sum(Deaths)) |> arrange((Deaths)) |> print(n = 5)
```

### Q.5) How many Confirmed , Deaths & Recovered cases were reported from India till 29 April 2020?

```{r}
covid |> filter(Region == 'India')
```

### Q. 6-A ) Sort the entire data wrt No. of Confirmed cases in ascending order

```{r}
covids |> arrange(Confirmed) |> print(n = 5)
```

### Q. 6-B ) Sort the entire data wrt No. of Recovered cases in descending order.

```{r}
covid |> arrange(desc(Recovered)) |>  print(n = 10)
```

## \### We have come to an End.
