---
title: "Weather Data Analysis"
author: 
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    keep_tex: yes
  word_document: default
  html_document: default
---
*******************************************************************************************
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
load(file = "King.RData")
```
```{r}
pacman::p_load(pacman, dplyr, GGally, ggplot2, ggthemes, 
               ggvis, httr, lubridate, plotly, rio, rmarkdown, shiny, 
               stringr, tidyr, reticulate, tidyverse, psych)
```
**********************************************************************************
# The Weather Dataset

Here, The Weather Dataset is a time-series data set with per-hour information about the weather conditions at a particular location. It records Temperature, Dew Point Temperature, Relative Humidity, Wind Speed, Visibility, Pressure, and Conditions.

This data is available as a CSV file.

```{r}
WeatherDataset
```

## .head()
It shows the first N rows in the data (by default, N=5).

```{r}
WeatherDataset |> 
  head()
```

## .shape

It shows the total no. of rows and no. of columns of the dataframe.

```{python}
r.WeatherDataset.shape
```

## .index

This attribute provides the index of the dataframe.

```{python}
r.WeatherDataset.index
```

## .columns

It shows the name of each column.

```{r}
WeatherDataset |> 
  colnames()
```

## .dtypes

It shows the data-type of each column.

```{r}
WeatherDataset |> 
  str()
```

with python code the output is

```{python}
r.WeatherDataset.dtypes
```

## .unique()

In a column, it shows all the unique values. It can be applied on a single column only, not on the whole dataframe.

```{r}
unique(WeatherDataset$Weather)
```
## .is.na

SHow the total number of non-null Values in each column. It can be applied in both the Dataframe and a single column

```{r}
sum(is.na(WeatherDataset$Weather))
```
In a column, it shows all the unique values with their count. It can be applied on single column only.

```{python}
r.WeatherDataset["Weather"].value_counts()
```

## .count
```{r}
WeatherDataset |> 
  count()
```

## .info()

Provides basic information about the dataframe.

```{r}
WeatherDataset |> 
  describe()
```
Lets Dive into Answering Some Useful Analysis Questions

-----------------------------------------------------------------------------------------------------------
# Weather Analysis

## Q) 1.  Find all the unique 'Wind Speed' values in the data.
```{r}
WeatherDataset |> 
  count(`Wind Speed_km/h`)
```
Using Unique
```{r}
unique(WeatherDataset$`Wind Speed_km/h`)
```
## Q) 2. Find the number of times when the 'Weather is exactly Clear'.
```{r}
WeatherDataset |> 
  filter(Weather == 'Clear') |> 
  count()
```
```{r}
WeatherDataset |> 
  filter(Weather == 'Clear')
```
## Q) 3. Find the number of times when the 'Wind Speed was exactly 4 km/h'.
```{r}
WeatherDataset |> 
  filter(`Wind Speed_km/h` == 4) |> 
  count()
```

```{r}
WeatherDataset |> 
  filter(`Wind Speed_km/h` == 4)
```
## Q. 4) Find out all the Null Values in the data.
```{r}
WeatherDataset |> 
  is.null()
```
This means that there are no null Values in the dataset
## Q. 5) Rename the column name 'Weather' of the dataframe to 'Weather Condition'.
```{r}
WeatherDataset |> 
  rename('Weather_Dataset' = 'Weather') |> 
  colnames()
```
## Q.6) What is the mean 'Visibility' ?
```{r}
WeatherDataset |> 
  describe()
```
Singularly
```{r}
mean(WeatherDataset$Visibility_km)
```
## Q. 7) What is the Standard Deviation of 'Pressure'  in this data?
```{r}
sd(WeatherDataset$Press_kPa)
```
## Q. 8) Whats is the Variance of 'Relative Humidity' in this data ?
```{r}
var(WeatherDataset$`Rel Hum_%`)
```
## Q. 9) Find all instances when 'Snow' was recorded.
looking for just the Instance "Snow"
```{r}
WeatherDataset |> 
  filter(`Weather` == 'Snow')
```
But when we want to get all the columns that has "Snow" in it we use ```grepl``` in R and ```str.contains``` in python
```{r}
WeatherDataset |> 
  filter(grepl('Snow', Weather))
```
## Q. 10) Find all instances when 'Wind Speed is above 24' and 'Visibility is 25'.
```{r}
WeatherDataset |> 
  filter((Visibility_km == 25) & ('Wind Speed_km/h' > 24))
```
## Q. 11) What is the Mean value of each column against each 'Weather Conditon' ?
```{r}
WeatherDataset |> 
  group_by(Weather) |> 
  summarise(across(Temp_C:Press_kPa, mean))
```
Though the code is longer using R, Python makes It Easy for us
```{python echo=TRUE}
r.WeatherDataset.drop('Date/Time', axis=1).groupby('Weather').mean()
```
The Date/Time column is recorded as a calculated column, so we hav to drop it
## Q. 12) What is the Minimum & Maximum value of each column against each 'Weather Conditon' ?
```{r}
WeatherDataset |> 
  group_by(Weather) |> 
  summarise(across(Temp_C:Press_kPa, min))
```
The Above is for the Minimun, The Maximum numbers include
```{r}
WeatherDataset |> 
  group_by(Weather) |> 
  summarise(across(Temp_C:Press_kPa, max))
```
Lets try python code
```{python echo=TRUE}
r.WeatherDataset.groupby('Weather').min()
```
## Q. 13) Show all the Records where Weather Condition is Fog.
```{r echo=TRUE}
WeatherDataset |> 
  filter(Weather == 'Fog')
```
## Q. 14) Find all instances when 'Weather is Clear' or 'Visibility is above 40'.
```{r echo=TRUE}
WeatherDataset |> 
  filter((Visibility_km > 40) & grepl('Clear', Weather))
```
## Q. 15) Find all instances when :
### A. 'Weather is Clear' and 'Relative Humidity is greater than 50'
### or
### B. 'Visibility is above 40'
```{r}
WeatherDataset |> 
  filter(grepl('Clear', Weather) & (`Rel Hum_%` > 50) | (Visibility_km > 40))
```

We have come to the End of the Descriptive Analysis.


By Precious Ikebude.

***********************************************************************